Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-28 src/article.tex
Revise acknowledgements

This work was supported by the National Institute for Health: IDeA Network of
Biomedical Research Excellence (KY-INBRE) grant: NIH 2P20 RR016481-09 and the
NIH R15 AREA Program grant: NIH R15GM079775.

>>>>

This work was supported by the National Institute for Health: IDeA Network of
Biomedical Research Excellence (KY-INBRE) grant (NIH 2P20 RR016481-09) and the
NIH R15 AREA Program grant (R15GM079775).
